### 2023-02-28 notebooks/conformal.qmd
uh
some work on configurable loss function

```{julia}
using CCE
using ConformalPrediction
using CounterfactualExplanations
using CounterfactualExplanations.Data
using Flux
using MLJBase
using MLJFlux
using Plots
```

@@

```{julia}
#| output: true
#| echo: false

ordered_names = [
    "Generic (γ=0.5)",
    "Generic (γ=0.9)",
    "Conformal (λ₂=1)",
    "Conformal (λ₂=10)"
]

>>>>

```{julia}
using CCE
using ConformalPrediction
using CounterfactualExplanations
using CounterfactualExplanations.Data
using CounterfactualExplanations.Objectives
using Flux
using MLJBase
using MLJFlux
using Plots
```

@@

### Penalizing Size

```{julia}
#| output: true
#| echo: false
#| label: fig-ce
#| fig-cap: "Comparison of counterfactuals produced using different generators."

opt = Descent(0.01)
ordered_names = [
    "Generic (γ=0.5)",
    "Generic (γ=0.9)",
    "Conformal (λ₂=1)",
    "Conformal (λ₂=10)"
]
loss_fun = Objectives.logitbinarycrossentropy

# Generators:
generators = Dict(
    ordered_names[1] => GenericGenerator(opt = opt, decision_threshold=0.5),
    ordered_names[2] => GenericGenerator(opt = opt, decision_threshold=0.9),
    ordered_names[3] => CCE.ConformalGenerator(loss=loss_fun, opt=opt, λ=[0.1,1]),
    ordered_names[4] => CCE.ConformalGenerator(loss=loss_fun, opt=opt, λ=[0.1,10]),
)

### Configurable Classification Loss

```{julia}
#| output: true
#| echo: false
#| label: fig-ce
#| fig-cap: "Comparison of counterfactuals produced using different generators."

opt = Descent(0.01)
ordered_names = [
    "Generic (γ=0.5)",
    "Generic (γ=0.9)",
    "Conformal (λ₂=1)",
    "Conformal (λ₂=10)"
]
loss_fun = Objectives.logitbinarycrossentropy
